Displacement of fishing effort by Large Scale Marine Protected Areas

### 2018-10-13 docs/Manuscript.tex
Updated intro

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Displacement of fishing effort by Large Scale Marine Protected Areas},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{plainnat}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Displacement of fishing effort by Large Scale Marine Protected Areas}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \subtitle{Updated on 2018-10-11}
  \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
Lynham\textsuperscript{2}}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{\textsuperscript{1}Bren School of Environmental Science and Management,
University of California Santa Barbara, Santa Barbara,
CA\newline \textsuperscript{2}Department of Economics, University of
Hawaii at Manoa, Honolulu, HI}

@@

Marine Protected Areas (MPAs) are intended to safeguard parts of the
ocean from extractive activities such as fishing. Current international
goals aim to ``effectively protect 10\% of the ocean environments by
2020''. In an effort to meet this target, the world has seen a rapid
increase in MPA coverage \citep{wood_2008,sala_2018b}. A significant
part of this rapid increase can be attributed to the designation of a
small number of Large Scale Marine Protected Areas {[}LSMPAs;
\citep{gray_2017}{]}. These are defined as MPAS with at least 250,000
km\textsuperscript{2} in extension \citep{toonen_2013}, and are often
implemented in the pelagic environment, where the dominant human
activity is industrial fishing \citep{gray_2017}.

Due to weak property rights, limited habitat transformation, and
potentially lower management costs, pelagic MPAs provide a great
opportunity to safeguard the oceans \citet{game_2009}{[}\^{}d{]}. A
growing body of literature has also shown that closing the high seas to
all fishing -effectively, turning them into a LSMPA- could increase
fishery yields and profitability of fisheries, without negligible costs
to food security
\citep{white_2014,sumaila_2015,sala_2018,schiller_2018}. However, as
with customary MPAs, it is important that we understand the
socioeconomic implications of management interventions.

Given the relatively recent establishment of most LSMPAs, very little is
known about their human dimensions and implication for fisheries
\citep{gray_2017}. LSMPAs were erroneously assumed to have little social
implications due to their remoteness \citep{agardy_2011,gray_2017}.
However, the anticipation of a LSMPA can lead to preemptive overfishing,
which can erode or delay the expected benefits of the intervention
\citep{mcdermott_2018}. LSMPAs have received great attention in terms of
governance and enforcement, but are yet to be the focus of economic
analyses \citep{gray_2017}. For example, \citet{mcdermott_2018} show
that fishing effort within the Phoenix Islands Marine Protected Area
(PIPA) is effectively reduced after implementation, and describe changes
in fishing behavior pre-implementation. \citet{cabral_2017} analyse the
redistribution of fishing and non-fishing vessels following the
implementation of MPAs in California, and find that responses are
idiosyncratic; commercial dive boats follow a fishing-the-line pattern,
while some fishing boats follow an ideal free distribution. The way in
which fishers react to a spatial closure can have major implications in
its outcome \citep{hilborn_2006,krueck_2017,viana_2017}. This highlights
the need to understand how fishers react to the implementation of a
LSMPA, and fishing effort changes and is spatially redistributed.

The main objective of this paper is to identify how fishers adapt to the
implementation of LSMPAs. We combine novel vessel tracking technologies
and causal inference techniques to identify behavioral changes of
fishing vessels due to the implementation of PIPA. We focus on fishing
hours and distance traveled as outcome variables that fishers might
adjust following implementation of a LSMPA in an impact-evaluation
fashion. Additionally, we evaluate the spatial redistribution of fishing
effort that existed within PIPA before its implementation. This work
provides novel empirical insights into fisher's responses to the
implementation of LSMPAs, and can help guide future interventions.

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-20-1.pdf}
\caption{\label{fig:unnamed-chunk-20}\label{fig:baci_strict}Stream of
fishing events by vessels through time. Each line represents a vessel,
with dots indicating months with fishing activity and colors indicating
the pre and post periods.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-21}\label{tab:baci_n_s}Number of fishing vessels and fishing hours by gear and treatment group before and after PIPA.}
\centering
\begin{tabular}[t]{llrrrr}
\toprule
Gear & Treatment & n & Before & After & Change (A / B)\\
\midrule
drifting\_longlines & FALSE & 77 & 39.03181 & 37.79044 & 0.9681958\\
drifting\_longlines & TRUE & 115 & 41.62659 & 40.43857 & 0.9714600\\
purse\_seines & FALSE & 26 & 11.73804 & 20.13247 & 1.7151474\\
purse\_seines & TRUE & 61 & 10.66939 & 18.36289 & 1.7210820\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-25-1.pdf}
\caption{\label{fig:unnamed-chunk-25}\label{fig:all_vessels}Fishing hours
and number of vessels by month for all vessels. Vertical dashed line
indicates PIPA closure.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-29-1.pdf}
\caption{\label{fig:unnamed-chunk-29}\label{fig:redist_trend_ps}Monthly
relative allocation of fishing effort by PIPA-fishing vessels before and
after PIPA for 9 EEZs, PIPA, the high seas and `other EEZs'.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-31-1.pdf}
\caption{\label{fig:unnamed-chunk-31}\label{fig:map_change_ps}Spatial
representation of the mean change in the monthly allocation of fishing
effort for purse seiners.}
\end{figure}

@@

\hypertarget{discusion}{%
\section{Discusion}\label{discusion}}

@@

\begin{verbatim}
## [[1]]
## 
## Call:
## lm(formula = hours ~ post * treated, data = data)
## 
## Coefficients:
##  (Intercept)          post       treated  post:treated  
##      11.7380        8.3944       -1.0687       -0.7009  
## 
## 
## [[2]]
## 
## Call:
## lm(formula = hours ~ post * treated + month_c, data = data)
## 
## Coefficients:
##  (Intercept)          post       treated     month_c10     month_c11  
##      11.2808        9.3338       -0.7699        2.8855        3.6875  
##    month_c12      month_c2      month_c3      month_c4      month_c5  
##       3.0010       -0.9889       -2.2384       -3.6433       -4.5904  
##     month_c6      month_c7      month_c8      month_c9  post:treated  
##      -4.4198       -3.5805        0.3173        2.8648       -0.8990  
## 
## 
## [[3]]
## 
## Call:
## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
## 
## Coefficients:
##  (Intercept)          post       treated     month_c10     month_c11  
##     13.94161       9.13865       0.04064       2.63902       3.55558  
##    month_c12      month_c2      month_c3      month_c4      month_c5  
##      2.59370      -1.06244      -2.41158      -4.00798      -4.91378  
##     month_c6      month_c7      month_c8      month_c9       flagECU  
##     -4.97737      -3.35106       0.20410       2.30467      -6.18817  
##      flagESP       flagFSM       flagKOR       flagMHL       flagOTH  
##     -2.94857      -4.72899      -3.70832      -1.87867      -2.24359  
##      flagTWN  post:treated  
##     -2.49301      -0.90817
\end{verbatim}

\begin{verbatim}
## [[1]]
## 
## Call:
## lm(formula = hours ~ post * treated, data = data)
## 
## Coefficients:
##  (Intercept)          post       treated  post:treated  
##     11.41504       8.22194      -0.01516      -2.01435  
## 
## 
## [[2]]
## 
## Call:
## lm(formula = hours ~ post * treated + month_c, data = data)
## 
## Coefficients:
##  (Intercept)          post       treated     month_c10     month_c11  
##      10.9718        8.6646        0.0589        3.1399        4.2030  
##    month_c12      month_c2      month_c3      month_c4      month_c5  
##       2.8778       -0.8801       -2.1805       -4.0561       -4.0234  
##     month_c6      month_c7      month_c8      month_c9  post:treated  
##      -4.7427       -4.4566        0.9716        4.9466       -2.0474  
## 
## 
## [[3]]
## 
## Call:
## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
## 
## Coefficients:
##  (Intercept)          post       treated     month_c10     month_c11  
##        8.160         8.923         2.910         3.489         4.775  
##    month_c12      month_c2      month_c3      month_c4      month_c5  
##        3.087        -1.082        -1.776        -4.186        -4.108  
##     month_c6      month_c7      month_c8      month_c9       flagMHL  
##       -5.336        -4.115         1.249         4.322         2.969  
## post:treated  
##       -2.984
\end{verbatim}

\begin{verbatim}
## [[1]]
## 
## Call:
## lm(formula = hours ~ post * treated, data = data)
## 
## Coefficients:
##  (Intercept)          post       treated  post:treated  
##      11.1998        9.0182       -0.5304       -1.3247  
## 
## 
## [[2]]
## 
## Call:
## lm(formula = hours ~ post * treated + month_c, data = data)
## 
## Coefficients:
##  (Intercept)          post       treated     month_c10     month_c11  
##     10.74814      10.57403      -0.03924       2.43719       3.37646  
##    month_c12      month_c2      month_c3      month_c4      month_c5  
##      2.62526      -1.19664      -2.77934      -3.76747      -4.65285  
##     month_c6      month_c7      month_c8      month_c9  post:treated  
##     -4.79738      -3.64640       0.15290       3.15125      -2.13569  
## 
## 
## [[3]]
## 
## Call:
## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
## 
## Coefficients:
##  (Intercept)          post       treated     month_c10     month_c11  
##      14.3391       10.4923        0.4295        2.2241        3.1505  
##    month_c12      month_c2      month_c3      month_c4      month_c5  
##       2.0719       -1.2564       -2.8501       -4.0129       -5.0320  
##     month_c6      month_c7      month_c8      month_c9       flagECU  
##      -5.3231       -3.4871       -0.2020        2.2869       -5.4622  
##      flagESP       flagFSM       flagKOR       flagMHL       flagOTH  
##      -3.3566       -1.4486       -4.2977       -2.3611       -3.3106  
##      flagTWN  post:treated  
##      -3.2657       -2.2534
\end{verbatim}

\begin{verbatim}
## [[1]]
## 
## Call:
## lm(formula = hours ~ post * treated, data = data)
## 
## Coefficients:
##  (Intercept)          post       treated  post:treated  
##      11.4202        7.8750       -0.7508       -0.1815  
## 
## 
## [[2]]
## 
## Call:
## lm(formula = hours ~ post * treated + month_c, data = data)
## 
## Coefficients:
##  (Intercept)          post       treated     month_c10     month_c11  
##      10.9725        8.7780       -0.4452        2.8476        3.6473  
##    month_c12      month_c2      month_c3      month_c4      month_c5  
##       3.0113       -1.1434       -2.4295       -3.5424       -4.4423  
##     month_c6      month_c7      month_c8      month_c9  post:treated  
##      -4.5243       -3.6704        0.2277        3.0019       -0.3310  
## 
## 
## [[3]]
## 
## Call:
## lm(formula = hours ~ post * treated + month_c + flag, data = flag_data)
## 
## Coefficients:
##  (Intercept)          post       treated     month_c10     month_c11  
##    14.036151      8.770151      0.557241      2.444760      3.320156  
##    month_c12      month_c2      month_c3      month_c4      month_c5  
##     2.456643     -1.307835     -2.707138     -4.024565     -4.841901  
##     month_c6      month_c7      month_c8      month_c9       flagECU  
##    -5.275270     -3.545459      0.001697      2.319940     -6.396277  
##      flagESP       flagFSM       flagKOR       flagMHL       flagOTH  
##    -3.432356     -4.833825     -4.212230     -1.836510     -3.284000  
##      flagTWN  post:treated  
##    -2.637666     -0.454598
\end{verbatim}

\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-1.pdf}
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-2.pdf}
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-3.pdf}
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-37-4.pdf}

>>>>

\documentclass[11pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Displacement of fishing effort by Large Scale Marine Protected Areas},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{natbib}
\bibliographystyle{plainnat}
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

  \title{Displacement of fishing effort by Large Scale Marine Protected Areas}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \subtitle{Updated on 2018-10-12}
  \author{Juan Carlos Villaseñor-Derbez\textsuperscript{1} John
Lynham\textsuperscript{2}}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{\textsuperscript{1}Bren School of Environmental Science and Management,
University of California Santa Barbara, Santa Barbara,
CA\newline \textsuperscript{2}Department of Economics, University of
Hawaii at Manoa, Honolulu, HI}

@@

Marine Protected Areas (MPAs) are intended to safeguard parts of the
ocean from fishing and other extractive activities. Current
international goals aim to ``effectively protect 10\% of the ocean
environments by 2020''. In an effort to meet this target, the world has
seen a rapid increase in MPA coverage \citep{wood_2008,sala_2018}. A
significant part of this rapid increase can be attributed to the
designation of a small number of Large Scale Marine Protected Areas
{[}LSMPAs; \citep{gray_2017}{]}. These are defined as MPAS with at least
250,000 Km\textsuperscript{2} in extension (Fig. \ref{fig:LSMPAs_map}),
and are often implemented in the pelagic environment, where the dominant
human activity is industrial fishing
\citep{toonen_2013,gray_2017,kroodsma_2018}.

Due to weak property rights, limited habitat transformation, and
potentially lower management costs, pelagic MPAs provide an opportunity
to safeguard the oceans \citet{game_2009}. A growing body of literature
has shown that closing the high seas to all fishing -effectively,
turning them into a LSMPA- could increase fishery yields and
profitability of fisheries, with negligible costs to food security
\citep{white_2014,sumaila_2015,sala_2018a,schiller_2018}. However, as
with customary MPAs, it is important that we understand the
socioeconomic implications of management interventions.

Given the relatively recent establishment of most LSMPAs, very little is
known about their human dimensions and implication for fisheries
\citep{gray_2017}. LSMPAs were erroneously assumed to have little social
implications due to their remoteness \citep{agardy_2011,gray_2017}.
However, the anticipation of a LSMPA can lead to preemptive overfishing,
which can erode or delay the expected benefits of the intervention
\citep{mcdermott_2018}. LSMPAs have received great attention in terms of
governance and enforcement, but are yet to be the focus of economic
analyses \citep{gray_2017}.

Research on LSMPAs have been the focus of analysing X, Y, and Z.
However, no studies look into displacement of fishing effort.
Redistribution of fishing effort has been evaluated in ssf by X, Y ,and
Z. \citet{cabral_2017} analyse the redistribution of fishing and
non-fishing vessels following the implementation of MPAs in California,
and find that responses are idiosyncratic; commercial dive boats follow
a fishing-the-line pattern, while some fishing boats follow an ideal
free distribution. The way in which fishers react to a spatial closure
can have major implications in its outcome
\citep{smith_2003,hilborn_2006}. This highlights the need to understand
how fishers react to the implementation of a LSMPA, and fishing effort
changes and is spatially redistributed.

The main objective of this paper is to identify how fishers change their
behavior due to the implementation of LSMPAs. We combine novel vessel
tracking technologies and causal inference techniques to identify
behavioral changes of fishing vessels due to the implementation of PIPA.
We focus on fishing hours and distance traveled as outcome variables
that fishers might adjust following implementation of a LSMPA in an
impact-evaluation fashion. Additionally, we evaluate the spatial
redistribution of fishing effort that existed within PIPA before its
implementation. This work provides novel empirical insights into
fisher's responses to the implementation of LSMPAs, and can help guide
future interventions. Our work is novel in the sense that it provides
empirical evidence of the effect of large-acale Marine Protected Areas
in fishing behavior and distribution.

The next sections are as follows: Section \ref{background} provides an
overview of the Nauru Agreement and associated countries, a description
of the fleet that operates in the region, and a brief history of PIPA.
Section \ref{methods} describes our data and identification strategy.
Section \ref{results} presents our results, section \ref{discussion}
provides an extension of our results to other LSMPAs and discusses our
results.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{\label{fig:unnamed-chunk-2}\label{fig:LSMPAs_map}}
\end{figure}

\hypertarget{background}{%
\section{Background}\label{background}}

The Nauru Agreement was established in 1982 by Pacific island nations to
manage their important tuna resources. PNA Members include Federated
States of Micronesia, Kiribati, Marshall Islands, Nauru, Palau, Papua
New Guinea, Solomon Islands, and Tuvalu.The Nauru Agreement regulated
access of foreign vessels (\emph{i.e.} those from non-PNA countries).
Holding \textasciitilde{}80\% of the historical purse seining grounds
within their Exclusive Economic Zones, PNA countries gained bargaining
power when providing access to foreign fleets \citep{havice_2010}.

The cooperation that emerged thanks to the PNA allowed for subsequent
agreements that strengthened fisheries management, like the Palau
Agreement, which limited the number of purse seiners at 205 vessels from
1995-2007\footnote{See \citet{havice_2010} for a detailed description of
  the Nauru, Palau, and Federal States of Micronesia agreements, their
  objectives, and outcomes.}. However, the most notable regulation is
their approach to manage fishing effort: a Vessel Day Scheme (VDS)
implemented in 2007 \citep{havice_2013}. This effectively modified how
fishing effort was managed, from number of vessels under the Palau
Agreement to fishing hours. The VDS works as follows: Each year,
scientific advisors recomend a total number of fishing vessel-days per
year. Hours are allocated to each PNA country based on catch history,
and they then sell fishing rights to other non-PNA countries
\citep{aqorau_2018}. While the effectiveness of this scheme has been
debated in terms of meeting their fishery management and conservation
objectives, the licensing significantly contributes to the economy of
these island nations \citep{havice_2010}.

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{\label{fig:unnamed-chunk-3}\label{fig:PNA_map}}
\end{figure}

The main tuna species caught in the region are skipjack
(\emph{Katsuwonus pelamis}), yellowfin (\emph{Thunnus albacares}),
albacore (\emph{Thunnus alalunga}) and bigeye (\emph{Thunnus obesus}).
From these, the first two are amongst the top-10 species represented in
global fisheries production statistics, with catches increasing relative
to the 2005-2014 average \citep{fao_2018}. The pacific region has
historically accounted for a large portion of tuna species production
\citep{aqorau_1997}. Today, the PNA controls close to 50\% of the global
skipjack tuna production \citep{pna_website_2018}. A large portion of
these catches derive from purse seine vessels licensed under the VDS.
Fishing vessels from Australia, New Zeland, China, France, Korea, Japan,
the Philippines, Taiwan and the United States participate in the
purse-seining vessel day schemes.

For example, \citet{mcdermott_2018} show that fishing effort within the
Phoenix Islands Marine Protected Area (PIPA) is effectively reduced
after implementation, and describe changes in fishing behavior
pre-implementation.

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-6-1.pdf}
\caption{\label{fig:unnamed-chunk-6}\label{fig:baci_strict}Stream of fishing
events by vessels through time. Each line represents a vessel, with dots
indicating months with fishing activity and colors indicating the pre
and post periods.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-7}\label{tab:baci_n_s}Number of fishing vessels and fishing hours by gear and treatment group before and after PIPA.}
\centering
\begin{tabular}[t]{llrrrr}
\toprule
Gear & Treatment & n & Before & After & Change (A / B)\\
\midrule
drifting\_longlines & FALSE & 77 & 39.03181 & 37.79044 & 0.9681958\\
drifting\_longlines & TRUE & 115 & 41.62659 & 40.43857 & 0.9714600\\
purse\_seines & FALSE & 26 & 11.73804 & 20.13247 & 1.7151474\\
purse\_seines & TRUE & 61 & 10.66939 & 18.36289 & 1.7210820\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-11-1.pdf}
\caption{\label{fig:unnamed-chunk-11}\label{fig:all_vessels}Fishing hours
and number of vessels by month for all vessels. Vertical dashed line
indicates PIPA closure.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-15-1.pdf}
\caption{\label{fig:unnamed-chunk-15}\label{fig:redist_trend_ps}Monthly
relative allocation of fishing effort by PIPA-fishing vessels before and
after PIPA for 9 EEZs, PIPA, the high seas and `other EEZs'.}
\end{figure}

\begin{figure}
\centering
\includegraphics{C:/Users/JC/Documents/GitHub/MPA_displacement/docs/Manuscript_files/figure-latex/unnamed-chunk-17-1.pdf}
\caption{\label{fig:unnamed-chunk-17}\label{fig:map_change_ps}Spatial
representation of the mean change in the monthly allocation of fishing
effort for purse seiners.}
\end{figure}

@@

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

@@

\begin{verbatim}
## 
## % Table created by stargazer v.5.2 by Marek Hlavac, Harvard University. E-mail: hlavac at fas.harvard.edu
## % Date and time: vie., oct. 12, 2018 - 06:16:13 p. m.
## \begin{table}[!htbp] \centering 
##   \caption{} 
##   \label{} 
## \begin{tabular}{@{\extracolsep{5pt}}lccc} 
## \\[-1.8ex]\hline 
## \hline \\[-1.8ex] 
##  & \multicolumn{3}{c}{\textit{Dependent variable:}} \\ 
## \cline{2-4} 
## \\[-1.8ex] & \multicolumn{3}{c}{hours} \\ 
## \\[-1.8ex] & (1) & (2) & (3)\\ 
## \hline \\[-1.8ex] 
##  post & 8.394$^{***}$ & 9.334$^{***}$ & 9.139$^{***}$ \\ 
##   & (0.271) & (0.265) & (0.300) \\ 
##   & & & \\ 
##  treated & $-$1.069$^{***}$ & $-$0.770$^{***}$ & 0.041 \\ 
##   & (0.259) & (0.253) & (0.317) \\ 
##   & & & \\ 
##  month\_c10 &  & 2.885$^{***}$ & 2.639$^{***}$ \\ 
##   &  & (0.302) & (0.335) \\ 
##   & & & \\ 
##  month\_c11 &  & 3.687$^{***}$ & 3.556$^{***}$ \\ 
##   &  & (0.304) & (0.335) \\ 
##   & & & \\ 
##  month\_c12 &  & 3.001$^{***}$ & 2.594$^{***}$ \\ 
##   &  & (0.309) & (0.339) \\ 
##   & & & \\ 
##  month\_c2 &  & $-$0.989$^{***}$ & $-$1.062$^{***}$ \\ 
##   &  & (0.308) & (0.334) \\ 
##   & & & \\ 
##  month\_c3 &  & $-$2.238$^{***}$ & $-$2.412$^{***}$ \\ 
##   &  & (0.313) & (0.340) \\ 
##   & & & \\ 
##  month\_c4 &  & $-$3.643$^{***}$ & $-$4.008$^{***}$ \\ 
##   &  & (0.317) & (0.345) \\ 
##   & & & \\ 
##  month\_c5 &  & $-$4.590$^{***}$ & $-$4.914$^{***}$ \\ 
##   &  & (0.316) & (0.349) \\ 
##   & & & \\ 
##  month\_c6 &  & $-$4.420$^{***}$ & $-$4.977$^{***}$ \\ 
##   &  & (0.332) & (0.368) \\ 
##   & & & \\ 
##  month\_c7 &  & $-$3.580$^{***}$ & $-$3.351$^{***}$ \\ 
##   &  & (0.336) & (0.366) \\ 
##   & & & \\ 
##  month\_c8 &  & 0.317 & 0.204 \\ 
##   &  & (0.311) & (0.346) \\ 
##   & & & \\ 
##  month\_c9 &  & 2.865$^{***}$ & 2.305$^{***}$ \\ 
##   &  & (0.309) & (0.341) \\ 
##   & & & \\ 
##  flagECU &  &  & $-$6.188$^{***}$ \\ 
##   &  &  & (0.434) \\ 
##   & & & \\ 
##  flagESP &  &  & $-$2.949$^{***}$ \\ 
##   &  &  & (0.497) \\ 
##   & & & \\ 
##  flagFSM &  &  & $-$4.729$^{***}$ \\ 
##   &  &  & (0.470) \\ 
##   & & & \\ 
##  flagKOR &  &  & $-$3.708$^{***}$ \\ 
##   &  &  & (0.289) \\ 
##   & & & \\ 
##  flagMHL &  &  & $-$1.879$^{***}$ \\ 
##   &  &  & (0.310) \\ 
##   & & & \\ 
##  flagOTH &  &  & $-$2.244$^{***}$ \\ 
##   &  &  & (0.290) \\ 
##   & & & \\ 
##  flagTWN &  &  & $-$2.493$^{***}$ \\ 
##   &  &  & (0.332) \\ 
##   & & & \\ 
##  post:treated & $-$0.701$^{**}$ & $-$0.899$^{***}$ & $-$0.908$^{***}$ \\ 
##   & (0.314) & (0.306) & (0.344) \\ 
##   & & & \\ 
##  Constant & 11.738$^{***}$ & 11.281$^{***}$ & 13.942$^{***}$ \\ 
##   & (0.229) & (0.313) & (0.422) \\ 
##   & & & \\ 
## \hline \\[-1.8ex] 
## Observations & 37,840 & 37,840 & 30,359 \\ 
## R$^{2}$ & 0.087 & 0.136 & 0.151 \\ 
## Adjusted R$^{2}$ & 0.087 & 0.136 & 0.150 \\ 
## Residual Std. Error & 12.752 (df = 37836) & 12.405 (df = 37825) & 12.257 (df = 30337) \\ 
## F Statistic & 1,203.929$^{***}$ (df = 3; 37836) & 427.020$^{***}$ (df = 14; 37825) & 256.286$^{***}$ (df = 21; 30337) \\ 
## \hline 
## \hline \\[-1.8ex] 
## \textit{Note:}  & \multicolumn{3}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
## \end{tabular} 
## \end{table}
\end{verbatim}
